Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-27 paper/main.tex
remove root from direct-comparison method
combine all figures into one large panel for amir

\begin{equation}
    L_{\text{LS}}(\vec{x}, \vec{y})
        = \sqrt{\sum\limits_{i,j,k}|\nu_{i,j,k} - \tilde{\nu}_{i,j,k}|^2}
\end{equation}

@@

\begin{figure}[H]
    \centering
    \begin{minipage}{0.38\textwidth}
        \begin{tikzonimage}[width=\textwidth]
            {figures/amir-elastic-000032-with-axes.png}%
            \node at (0.01, 0.01+17pt)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
        \end{tikzonimage}%
    \end{minipage}%
    \begin{minipage}{0.62\textwidth}
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-reduced/fit-comparison.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/drag_force.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/growth_rate.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
        \end{tikzonimage}\\
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/rod_rigidity.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/spring_tension.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/damping.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
        \end{tikzonimage}%
    \end{minipage}
    \caption{
        (A) Microscopic image containing a single bacterium which is partially confined in a narrow
        tube on the bottom and free at the top where a controlled flow can be exerted on them.
        Division of the bacteria is inhibited.
        (B) A comparison of the initial and bent state show good visual agreement of our prediction
        with the experimental data.
        (C-G) Likelihood profiles for the individual parameters before and after performing model
        reduction.
    }
    \label{fig:amir-bending-simulation}
\end{figure}

>>>>

\begin{equation}
    L_{\text{LS}}(\vec{x}, \vec{y})
        = \sum\limits_{i,j,k}|\nu_{i,j,k} - \tilde{\nu}_{i,j,k}|^2
\end{equation}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/progressions/step4-000010.png}
        \node at (0.02,17pt)[anchor=north west, white, draw, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/progressions/step4-000017.png}
        \node at (0.02,17pt)[anchor=north west, white, draw, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/progressions/step4-000034.png}
            \node at (0.01, 0.01+17pt)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles-reduced/fit-comparison.pdf}%
        \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles/drag_force.pdf}%
        \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles/growth_rate.pdf}%
        \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles/rod_rigidity.pdf}%
        \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles/spring_tension.pdf}%
        \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_amir/profiles/damping.pdf}%
        \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{H}};
    \end{tikzonimage}%
    \caption{
        \textbf{TODO fix caption numbers and add missing stuff}
        (A) Microscopic image containing a single bacterium which is partially confined in a narrow
        tube on the bottom and free at the top where a controlled flow can be exerted on them.
        Division of the bacteria is inhibited.
        (B) A comparison of the initial and bent state show good visual agreement of our prediction
        with the experimental data.
        (C-G) Likelihood profiles for the individual parameters before and after performing two
        successive model reductions.
        The first step removes any damping effects by settings $\lambda=0$ while the second fixes
        the spring tension to its calculated optimum $\gamma=\gamma_\text{opt}$.
    }
    \label{fig:amir-bending-simulation}
\end{figure}
